
title: "Mock_Results"
author: "Becca"
date: "7 augustus 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read in the mock field and mesocosm dataframes; load libraries.
```{r echo=FALSE}
library(tidyverse)
library(picante)
library(ggplot2)
setwd(getwd())

field<-read.csv2("~/Research/Data/Field_mockdata2.csv", header=TRUE)
library(readr)
meso <- read_csv("C:/Users/rbs335/surfdrive/Research/HollandseHout_Project/HH_R/Data/meso.csv")

meso$Sample_ID = as.factor(meso$Sample_ID)
meso$litter=as.factor(meso$litter)
meso$micro=as.factor(meso$micro)
meso$sterile=as.factor(meso$sterile)
meso$root=as.factor(meso$root)
meso$Time=as.factor(meso$Time)
meso$Rep=as.factor(meso$Rep)
View(meso)
```


Field data. Test for:
1)significant variation among species (litter traits, soil traits)
2)significant variation in soil carbon partitioning by depth and soil fraction
```{r echo=FALSE}
m1<-aov(CN_soil~Species, data=field)
summary(m1)

m1plot<-ggplot(field, aes(Species, CN_soil)) +
  geom_boxplot()+
  geom_point()
m1plot

m2<-aov(CN_litter~Species, data=field)
summary(m2)

m2plot<-ggplot(field, aes(Species, CN_litter)) +
  geom_boxplot() +
  geom_point()
m2plot

pm1m2<-ggplot(field, aes(CN_litter, CN_soil)) +
  geom_point() +
  facet_wrap(~Species) +
  geom_smooth(method="lm")
pm1m2

###Manova for AOV for the 4 proportions of soil by depth###
y<-cbind(field$PctDOC, field$Pct_MAOM, field$pct_POM, field$PCT_SAOM)

fit1<-manova(y~field$Depth)
summary(fit, test="Pillai")

fit2<-manova(y~Depth + Species, data=field)
summary(fit2)

##PERMANOVA
mod1<-adonis(y~Depth + Species, data=field, by=NULL)
mod1

mod2<-metaMDS(y)
mod2
plot(mod2)
```

Linear mixed-effect model:
```{r }
library(lme4)
library(nlme)
library(lsmeans)
maomfit<-lmer(Pct_MAOM ~ Species + (1|Depth), data=field)
maomfit
maomfit.aov<-anova(maomfit)
summary(maomfit.aov)
#lsmeans(maomfit.aov)

boxplot(field$Pct_MAOM~field$Depth)
```

Multivariate Analysis
```{r echo=FALSE}
library(MASS)

soil.lda <- lda(field$Pct_MAOM ~ field$Species + field$Depth + field$pH_Soil + field$pH_litter + field$TOC.g.kg. + field$TON.g.kg.)
soil.lda

```

Mesocosms - soil aggregation over time:
```{r }
meso$Time=as.factor(meso$Time)
library(nlme)
library(lme4)
library(pander)
agg<-lmer(pct_agg~Time + (1|litter), data=meso)
agg

###compare group means from linear hypothesis tests (ie, time 1 vs time 2, time 3 vs time 2)###
library(multcomp)
summary(glht(agg, linfct = mcp(Time = "Tukey")), test = adjusted("holm"))

###Significant differences among each time group, suggesting that aggregation increases from time point 1 to 2 and from 2 to 3. let's graph it:

agg.plot<-ggplot(agg, aes(x=Time, y=pct_agg)) +
          geom_point() +
          geom_boxplot()+
         xlab("Sampling period") +
         ylab("Percent aggregation by dry weight") 
agg.plot
```



Mesocosms - soil aggregation by species
```{r echo=FALSE}

agg2<-lmer(pct_agg~litter + Time + (1|root), data=meso)
summary(agg2)
plot(agg2)
###compare group means from linear hypothesis tests (ie, time 1 vs time 2, time 3 vs time 2)###

summary(glht(agg2, linfct = mcp(litter = "Tukey")), test = adjusted("holm"))

###Species a and b are significantly different, as are species a and c, but species b and c are not significantly different in their production of aggregation. 
meso.sub<-subset(meso, litter= "o")
                  
                  
agg2.plot<-ggplot(agg2, aes(x=litter, y=pct_agg)) +
          geom_point() +
          geom_boxplot() +
          facet_wrap(sterile~Time)
agg2.plot

```
  
  Microbial community growth efficiency by time and by speicies:
```{r echo=FALSE}
mic<-aov(mic_ge~litter + Time, data=meso)
summary(mic)
#significant variation among groups by species and time

#plot the boxplots
mic.time<-ggplot(mic, aes(x=Time, y=mic_ge)) +
    geom_boxplot() 

mic.time

mic.sp<-ggplot(mic, aes(x=litter, y=mic_ge)) +
  geom_boxplot() 
 # facet_wrap(~root)
mic.sp

#test the specific effects of time and species
mic.lmer<-lmer(mic_ge~litter + Time + (1|Rep), data=meso)
mic.lmer
#residuals look good. 
plot(mic.lmer)
#post-hoc tests
summary(glht(mic.lmer, linfct = mcp(litter = "Tukey")), test = adjusted("holm"))
summary(glht(mic.lmer, linfct = mcp(Time = "Tukey")), test = adjusted("holm"))
#Significant differences in microbial growth efficiency both with different species and over time. Now let's test teh relationship between growth efficiency and aggregation.
```

Aggregation as function of microbial community growth efficiency:
```{r echo=FALSE}
#microbial community growth efficiency and aggregation:
agg.mic<-lmer(pct_agg~mic_ge + (1|litter) + (1|Time), data=meso)
summary(agg.mic)
plot(agg.mic)
#residuals okay, some high points causing variation

#make the plot
agg.mic.plot<-ggplot(agg.mic, aes(x=mic_ge, y=pct_agg)) +
                 #can't get this to work, leave out for now: geom_point(color='meso$Species') +
                geom_point()  +
                geom_smooth(method = "lm") +
                xlab("Microbial community growth efficiency") +
                ylab("Percent aggregation by dry weight") 
agg.mic.plot

agg.time<-lmer(pct_agg~Time + (1|litter) + (1|mic_ge), data=meso)
summary(agg.time)
plot(agg.time)
#residuals okay, some high points causing variation

#make the plot
agg.mic.plot<-ggplot(agg.mic, aes(x=mic_ge, y=pct_agg)) +
                 #can't get this to work, leave out for now: geom_point(color='meso$Species') +
                geom_point()  +
                geom_smooth(method = "lm") +
                xlab("Microbial community growth efficiency") +
                ylab("Percent aggregation by dry weight") 
agg.mic.plot

```

Total SOC by treatment
```{r }
meso$trt<-paste(meso$litter, meso$micro, meso$root)
meso.sub<-subset(meso, litter_remain > "0")

me.mod<-lm(TOC ~ trt + Time, data=meso.sub)
summary(me.mod)

me.mod.aov<-aov(me.mod)
summary(me.mod.aov)

me.mod2<-lmer(TOC ~litter + (1|root) + (1|micro), data=meso)
summary(me.mod2)

me.mod3<-lmer(TOC ~ root + (1|litter) + (1|micro), data=meso)
summary(me.mod3)

me.box<-ggplot(meso.sub, aes(x = litter, y = TOC)) +
  geom_boxplot() +
  geom_point() +
  facet_wrap (micro ~ root)
me.box
```


Multivariate Analysis:
```{r }
my<-cbind(meso$DOC, meso$MAOM, meso$POM, meso$SAOM)
my.sub<-cbind(meso.sub$DOC, meso.sub$MAOM, meso.sub$POM, meso.sub$SAOM, meso.sub$rMAOM)
#View(my)

mymod1<-adonis(my.sub ~ litter + micro + Time, data = meso.sub, by=NULL)
mymod1

mymod2<-adonis(my.sub ~ litter:micro, data=meso.sub, by=NULL)
mymod2
```

```{r }

meso.root<-aov(TOC ~ root + litter  + Time, data=meso)
summary(meso.root)

root.meso<-subset(meso, litter=="o")
View(root.meso)

root.plot<-ggplot(root.meso, aes(x=root, y=TOC)) +
  geom_boxplot() +
  geom_point() +
  facet_wrap(~Time)
root.plot  

```
Treatment combination effects:
```{r }

tr.maom<-lm(MAOM ~trt + Time, data=meso)
summary(tr.maom)

tr.saom<-lm(SAOM ~trt + Time, data=meso)
summary(tr.maom)

root<-ggplot(meso, aes(x=root, y=TOC)) +
  geom_boxplot()+
  geom_point()
root

r.pom<-ggplot(meso, aes(x=root, y=POM)) +
  geom_boxplot()+
  geom_point()
r.pom

r.SAOM<-ggplot(meso, aes(x=root, y=SAOM)) +
  geom_boxplot()+
  geom_point()
r.SAOM

leaf.TOC<-ggplot(meso.sub, aes(x=litter, y=TOC)) +
  geom_boxplot() +
  geom_point ()
leaf.TOC

leaf.SAOM<-ggplot(meso.sub, aes(x=litter, y=SAOM)) +
  geom_boxplot() +
  geom_point ()
leaf.SAOM

```





